Text as Policy: Identifying Equivalent State Bills through Text Reuse

### 2016-02-10 manuscript/text_reuse.tex
revised intro

\title{Text as Policy: Identifying Equivalent State Bills through Text Reuse. \large Subtitle.}
\date{\today}
\author{Bruce Desmarais, Matt Burgess, Fridolin Linder, Eugenia Giraudi}

@@

The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}. Research on public policy adoption and diffusion has conventionally relied on modest hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}. In this paper we draw upon a massive and nearly all-encompassing source of data with which to measure the consideration and adoption of similar policies -- the text of legislation considered in US state legislatures. We take an automated, computer-based, approach to the analysis of bill text. This vastly increases the volume of data that can be included in policy diffusion research.

Through the development of automated text-analytic methods of measuring policy diffusion we consider several methodological challenges and broader conceptual hurdles. The central methodological puzzles are two-fold. First, we need to extract the substantive text of the legislation---minimizing the affect of procedural text on our measures of text reuse. Second, we need to develop a method for quantitatively scoring the reused text between bills. The main conceptual puzzle with which we engage is the potential ambiguity regarding whether two policies should be considered the same for the purpose of policy diffusion research. We cannot define a standard in the literature according to which two policies can be deemed equivalent, and argue instead for conceptualizing policy diffusion in terms of a continuum of similar policy rather than a dichotomy of equivalence.

We take a multi-pronged approach to evaluating the performance of text reuse in measuring the consideration and adoption of similar laws. First, we use topic modeling on the discovered reused text sequences to assess the content of the matching text. Second, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills. Third, we assess the how well policy diffusion networks that have been established by previous research can be predicted using the amount of text reuse between states. And fourth, we use data on equivalent bills collected by the National Council of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap.

This work has several important implications. First, it allows us to estimate, how policies are transferred between states. Do state legislators work mainly from templates from other states or interest groups, or to what extent do legislators draft their own bill text. Furthermore, text reuse is a relatively simple metric to calculate for large amounts of text. Previous scholars of policy diffusion mainly relied on case studies or manually coded data sets of policy diffusion in few policy areas. If working copying text forms a significant portion of how legislators adopt policies from other states, text reuse can be used to easily gather comprehensive data sets on policy diffusion.

>>>>

\title{Text as Policy: Identifying Equivalent State Bills through Text Reuse}
\date{\today}
\author{Bruce Desmarais, Matt Burgess, Fridolin Linder, Eugenia Giraudi}

@@

The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}. Research on public policy adoption and diffusion has conventionally relied on modestly-sized, hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}. In this paper we draw upon a voluminous and comprehensive source of data with which to measure the consideration and adoption of similar policies -- the text of legislation considered in US state legislatures. We take an automated, text-as-data, approach to the analysis of bill text. This vastly increases the volume of data that can be included in policy adoption research.

Through the development of automated text-analytic methods of measuring policy diffusion we consider several methodological challenges and broader conceptual hurdles. The central methodological puzzles are two-fold. First, we need to extract the substantive text of the legislation---minimizing the affect of procedural text on our measures of text reuse. Second, we need to develop a method for quantitatively scoring the reused text between bills. The main conceptual puzzle with which we engage is the potential ambiguity regarding whether two policies should be considered the same for the purpose of policy diffusion research. Considering precedents in the literature, we argue for conceptualizing policy adoption in terms of a continuum of similar policy rather than a dichotomy of equivalence.

We take a multi-pronged approach to evaluating the performance of text reuse in measuring the consideration and adoption of similar laws. First, we use topic modeling on the discovered reused text sequences to assess whether the content of the matching text follows major themes of public policy. Second, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills. Third, we assess the how well policy diffusion networks that have been established by previous research can be predicted using the amount of text reuse between states. And fourth, we use data on equivalent bills collected by the National Council of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap.
